Succinct representations for abstract interpretation

### 2011-11-02 papers/PLDI2012/implicitization.tex

We experimented with a heuristic
of dynamic construction of the $\sigma_i$ functions, adapted from
\citet{DBLP:conf/pldi/GulwaniZ10}. 
%\DM{Cette heuristique, je croyais que c'était nous qui l'avions trouvée,
%et qu'elle n'était pas dans Gulwani?}
%\JH{Non. Gulwani fait la même chose en un peu plus complique (voir commentaire
%suivant)}
%\MM{Du coup, la contribution~\ref{contr:disjunctive} devrait être
%  affaiblie un peu je suppose. Gulwani fait aussi du SMT-solving ?}
%\DM{Non, Gulwani énumère tous les chemins un par un à tous les coups.}

For each control point $p_i \in P_R$, we start with one single disjunct
($m_i = 1$) and define $\delta_i = 1$.
$M$ denotes an upper bound on the number of disjuncts per control point.

The $\sigma_i$ functions take as parameters the index of the starting abstract
value, and the path we focus on. 
Since we dynamically construct these functions
during the analysis, we store their already comupted image into a
compact representation, such as Algebraic Decision Diagrams.
$\sigma_i(j,k)$ is then constructed on the fly only when needed, and computed
only once.
When the value of $\sigma_i(j,k)$ is required but undefined, we first compute
the image of the
abstract value $X_{i,j}$ by the path indexed by $k$, and try to find an existing
disjunct of index $j'$ so that the least upper bound of the two abstract values is exactly their union (this can be tested using SMT-solving).
If such an index exists, then we set $\sigma_i(j,k) = j'$.
Otherwise:
\begin{itemize}[itemsep=-1\parsep,topsep=0pt]
	\item if $m_i < M$, we increase $m_i$ by $1$ and define $\sigma_i(j,k) = m_i$
	\item if $m_i = M$, we define $\sigma_i(j,k) = M$ 
		%\JH{A la place, Gulwani cherche l'invariant qui a le plus de contraintes
		%d'egalite en commun pour definir son $sigma$. Nous, on le met dans M, pour simplifier}
\end{itemize}

>>>>

We experimented with a heuristic
of dynamic construction of the $\sigma_i$ functions, adapted from
\citet{DBLP:conf/pldi/GulwaniZ10}. 
\DM{Cette heuristique, je croyais que c'était nous qui l'avions trouvée,
et qu'elle n'était pas dans Gulwani?}
\JH{Non. Gulwani fait la même chose en un peu plus complique (voir commentaire
suivant)}
\MM{Du coup, la contribution~\ref{contr:disjunctive} devrait être
  affaiblie un peu je suppose. Gulwani fait aussi du SMT-solving ?}
\DM{Non, Gulwani énumère tous les chemins un par un à tous les coups.}
\MM{OK, du coup j'ai ajouté une phrase à la fin de la section pour
  rappeler notre contrib}
For each control point $p_i \in P_R$, we start with one single disjunct
($m_i = 1$) and define $\delta_i = 1$.
$M$ denotes an upper bound on the number of disjuncts per control point.

The $\sigma_i$ functions take as parameters the index of the starting abstract
value, and the path we focus on. 
Since we dynamically construct these functions
during the analysis, we store their already comupted image into a
compact representation, such as Algebraic Decision Diagrams.
$\sigma_i(j,k)$ is then constructed on the fly only when needed, and computed
only once.
When the value of $\sigma_i(j,k)$ is required but undefined, we first compute
the image of the
abstract value $X_{i,j}$ by the path indexed by $k$, and try to find an existing
disjunct of index $j'$ so that the least upper bound of the two abstract values is exactly their union (this can be tested using SMT-solving).
If such an index exists, then we set $\sigma_i(j,k) = j'$.
Otherwise:
\begin{itemize}[itemsep=-1\parsep,topsep=0pt]
	\item if $m_i < M$, we increase $m_i$ by $1$ and define $\sigma_i(j,k) = m_i$
	\item if $m_i = M$, we define $\sigma_i(j,k) = M$ 
		%\JH{A la place, Gulwani cherche l'invariant qui a le plus de contraintes
		%d'egalite en commun pour definir son $sigma$. Nous, on le met dans M, pour simplifier}
\end{itemize}
The main difference with the original
algorithm~\cite{DBLP:conf/pldi/GulwaniZ10} is that we construct
$\sigma_i(j,k)$ using SMT queries instead of enumerating a possibly
exponential number of paths to find a solution.
